Less Funding, More Lecturers, and Fewer Professors: \\ \vspace{0.1cm} Stagnating State Funding for Higher Education and its Effect on Faculty

### 2024-09-25 text/sections/02-data.tex
Made some edits.

    These two major differences explain the different conclusions that our contemporary papers come to; \autoref{sec:recession-analysis} replicates the \cite{hinrichs2022state} empirical findings with my primary specification, and further discuses the differences in findings.

>>>>

    These two major differences explain the different conclusions that our contemporary papers come to; in \autoref{sec:recession-analysis} I replicate the \cite{hinrichs2022state} approach with my primary specification, and further discuses the differences in findings.
